\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Salem Al-Bream} % Your Name
\newcommand{\course}{Senior Software Engineer} % Your Program

\newcommand{\phone}{+962-78-6055238} % Your Phone Number
\newcommand{\emaila}{salemalbream@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ \phone}\\
  Senior Software Engineer { } & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
  Bachelor of Electrical Engineering & \href{https://github.com/salembream}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile: salembream}} \\  
  {Jordan University} & %-- \href{www.linkedin.com/in/xxxx/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}
\end{tabularx}
}


%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart

%%%%
%%%%


      \resumeSubheading
         {Senior Software Engineer} {Full Time}
         {Apryse Software Inc, Denver, Colorado}{(Feb 2024 - Present) Amman, Jordan Dept.} 
         \resumeItemListStart
      \item {Working on several Smart Document Understanding and image processing products.}
      \resumeItemListEnd
       
      \vspace{-2.0mm}
       
      \resumeSubheading
         {Senior Software Engineer} {Full Time}
         {LEAD Technologies Inc, Charlotte, North Carolina USA}{(Sep 2022 - Feb 2024) Amman, Jordan Dept.}
         \resumeItemListStart
      \item {Worked on different image processing and analysis products, such as Smart Document Understanding products, along with maintaining parts of the image processing SDK.}
      \resumeItemListEnd
       
      \vspace{-2.0mm}
          
      \resumeSubheading
         {Software Engineer}{Full Time}
         {AfkarDigital, Amman, Jordan}{(Mar 2019 - Sep 2022)}
         \resumeItemListStart
      \item {Design the architecture for different IoT systems and implement them, such IIoT (Industrial-IoT), Home Automation, Medical Equipment Monitoring and Data Centers Environment Monitoring.}
      \item {Dealing with MQTT/s, Modbus RTU/TCP, BLE and HTTP/s protocols.}
      \item {Contributed to our SQL Database and back-end services and refactored the front-end for some projects which required high performance and high stability.}
      \resumeItemListEnd
       
      \vspace{-2.0mm}

      \resumeSubheading
         {Research Assistant}{Part Time}
         {Jordan University - Faculty of Engineering}{(Dec 2019 - Oct 2020)}
         \resumeItemListStart
        \item {Worked with Prof. Mohammad Hawa, from Jordan University, Electrical Engineering Dept}
        \item {Contributed to the project (ns3++: GUI for the ns-3 networks simulator). My responsibility was to develop a code generator tool to auto generate C++ code based on the visual network built by the user.}
      \resumeItemListEnd
       
      \vspace{-2.0mm}

      \resumeSubheading
         {AI Model Trainer}{Part Time Remote Contractor}
         {OpenAI LP, California USA (through Turing.com Company)}{(Oct 2022 - Apr 2023) }
         \resumeItemListStart
      \item {Train AI models to solve puzzles and problem sets to enable the model to analyze the problem, its requirements, and its constraints, to find a valid solution and generate high-quality codes to implement it.}
      \item {Train AI models on how to test the generated codes, and to find the possible corner cases in the prompt problem, and also analyze the time complexity for the solution.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

      \vspace{-2.0mm}

      
%%%%
%%%%





%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor's degree in electrical engineering}{GPA: 3.53}
      {Jordan University}{2014-2019}
    \resumeSubheading
      {Jordan Tawjihi (Scientific Stream)}{Average: 95.2}
      {Salah Aldeen Secondary School}{2013/2014}
    \resumeSubHeadingListEnd

\vspace{-5.5mm}
%



%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, JavaScript/TypeScript, C\#/dotnet, Python}\\
     \textbf{Frameworks}{: ReactJs, ASP.net, LEADTOOLS, PyQt/PySide }\\ 
     \textbf{Soft Skills}{: Problem Solving, Self-learning, Presentation, Adaptability} \\
    }}
 \end{itemize}
 \vspace{-16pt}





%-----------Languages-----------------
\section{\textbf{Languages}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Arabic}{: Native Speaker }\\ 
     \textbf{English}{: Proficient }\\
    }}
 \end{itemize}
 \vspace{-16pt}




% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}



%-------------------------------------------
\end{document}
